```{r library, include=FALSE}
my_packages <- c("tidyverse", "data.table", "readxl",
                 "plyr",
                 "PharmacoGx")
pacman::p_load(char = my_packages)

tmp <- list()
```

# GDSC
## Cell anno
```{r}
gdsc_anno <- read_xlsx("Input/Datasets/GDSC/CellLineInfo.xlsx", sheet = 2)
gdsc_anno <- na.omit(gdsc_anno)
colnames(gdsc_anno) <- c("Barcode", "Source1", "Source2", "Name")
gdsc_anno$Barcode <- paste0("COSMIC_", gdsc_anno$Barcode)

table(gdsc_anno$Source1)
table(gdsc_anno$Source2)
```

Select leukemia-related cell lines:
```{r}
gdsc_anno2 <- gdsc_anno[gdsc_anno$Source1 %in% "leukemia",]

# gdsc_anno3 <- gdsc_anno2[gdsc_anno2$Barcode %in% colnames(gdsc_exp),]
```

```{r}
gdsc_anno_leu <- gdsc_anno2
```

## mRNA
```{r}
# Exp
gdsc_exp <- fread("Input/Datasets/GDSC/Cell_line_RMA_proc_basalExp.txt")
gdsc_exp <- as.data.frame(gdsc_exp)
gdsc_exp <- aggregate(.~GENE_SYMBOLS,max,data=gdsc_exp)
gdsc_exp[gdsc_exp$GENE_SYMBOLS %in% "",]$GENE_title
gdsc_exp[gdsc_exp$GENE_SYMBOLS %in% "",]$GENE_SYMBOLS <- "ZNF286A"

gdsc_exp$GENE_title <- NULL
rownames(gdsc_exp) <- gdsc_exp$GENE_SYMBOLS; gdsc_exp$GENE_SYMBOLS <- NULL
colnames(gdsc_exp) <- gsub("DATA.", "COSMIC_", colnames(gdsc_exp))
gdsc_exp[1:5,1:5]
```


```{r}
gdsc_exp_leu <- gdsc_exp[,colnames(gdsc_exp) %in% gdsc_anno_leu$Barcode]
```

```{r}
gdsc_anno_leu2 <- gdsc_anno_leu[match(colnames(gdsc_exp_leu), 
                                      gdsc_anno_leu$Barcode),]
colnames(gdsc_exp_leu) <- gdsc_anno_leu2$Name
```


## Mut
```{r}
gdsc_omics <- readRDS("Input/Datasets/GDSC/gdsc_omics.Rds")

gdsc_mut <- gdsc_omics$mutation_exome@assays@data$exprs

gdsc_mut_leu <- as.data.frame(gdsc_mut[,colnames(gdsc_mut) %in% gdsc_anno_leu$Name])
gdsc_mut_leu$genes <- rownames(gdsc_mut_leu)
gdsc_mut_leu <- gather(data = gdsc_mut_leu,
                     key = cells,
                     value = mutation,
                     - genes)
gdsc_mut_leu <- gdsc_mut_leu[!gdsc_mut_leu$mutation %in% "wt",]
```

## CNV
```{r}
gdsc_cnv <- gdsc_omics$cnv@assays@data$exprs

gdsc_cnv_leu <- as.data.frame(gdsc_cnv[,colnames(gdsc_cnv) %in% gdsc_anno_leu$Name])
```

## fusion
```{r}
gdsc_fusion <- gdsc_omics$fusion@assays@data$exprs
gdsc_fusion_leu <- as.data.frame(gdsc_fusion[,colnames(gdsc_fusion) %in% gdsc_anno_leu$Name])
gdsc_fusion_leu$genes <- rownames(gdsc_fusion_leu)
gdsc_fusion_leu <- gather(data = gdsc_fusion_leu,
                     key = cells,
                     value = fusion,
                     - genes)
gdsc_fusion_leu <- na.omit(gdsc_fusion_leu)
gdsc_fusion_leu <- gdsc_fusion_leu[!gdsc_fusion_leu$fusion %in% "wt",]
gdsc_fusion_leu$fusion <- NULL
colnames(gdsc_fusion_leu)[1] <- "fusion"
```

## Drugs
```{r}
gdsc_drug_raw <- fread("Input/Datasets/GDSC/sanger-dose-response.csv")
gdsc_drug <- gdsc_drug_raw[,c(
                          "DATASET",
                          "COSMIC_ID",
                          "DRUG_NAME",
                          "auc")]
gdsc_drug <- as.data.frame(gdsc_drug)
gdsc_drug$COSMIC_ID <- paste0("COSMIC_", gdsc_drug$COSMIC_ID)
```

```{r}
table(gdsc_anno_leu$Barcode %in% gdsc_drug$COSMIC_ID)
```

Select leukemia:
```{r}
gdsc_drug_leu <- gdsc_drug[gdsc_drug$COSMIC_ID %in% gdsc_anno_leu$Barcode,]
```

Split GDSC1, GDSC2:
```{r}
table(gdsc_drug_leu$DATASET)
```

```{r}
gdsc1_drug_leu <- gdsc_drug_leu[gdsc_drug_leu$DATASET %in% "GDSC1",]
gdsc1_drug_leu$DATASET <- NULL
gdsc1_drug_leu <- dcast(data.table(gdsc1_drug_leu), COSMIC_ID~DRUG_NAME,
                 value.var="auc", fun.aggregate = max, fill = NA)

gdsc2_drug_leu <- gdsc_drug_leu[gdsc_drug_leu$DATASET %in% "GDSC2",]
gdsc2_drug_leu$DATASET <- NULL
gdsc2_drug_leu <- dcast(data.table(gdsc2_drug_leu), COSMIC_ID~DRUG_NAME,
                 value.var="auc", fun.aggregate = max, fill = NA)
```

```{r}
changeName <- function(df1, df2, col1, col2){
  df1 <- as.data.frame(df1); df2 <- as.data.frame(df2)
  df2 <- df2[match(df1[, col1], df2[, col1]),]
  df1[,col1] <- df2[,col2]
  return(df1)
}
```

```{r}
gdsc_anno_leu$Name2 <- gsub("-", "", gdsc_anno_leu$Name)

# GDSC
gdsc_anno_leu$COSMIC_ID <- gdsc_anno_leu$Barcode
gdsc1_drug_leu <- changeName(df1 = gdsc1_drug_leu,
                              df2 = gdsc_anno_leu,
                              col1 = "COSMIC_ID",
                              col2 = "Name2")
gdsc2_drug_leu <- changeName(df1 = gdsc2_drug_leu,
                              df2 = gdsc_anno_leu,
                              col1 = "COSMIC_ID",
                              col2 = "Name2")
```

## Drugs anno
```{r}
# gdsc_drug_anno <- gdsc_drug_raw[,c("DATASET",
#                                "DRUG_NAME",
#                                "DRUG_ID")]
# gdsc_drug_anno <- unique(gdsc_drug_anno)
# gdsc_drug_anno <- gdsc_drug_anno[!gdsc_drug_anno$DRUG_NAME %in% "",]
```

## Cell anno
add cell line anno info ref by ccle:
```{r}
# ccle_anno_leu
gdsc_anno_leu2 <- merge(gdsc_anno_leu,
                       ccle_anno_leu[,c(2,6,7)], by.x = "Name2",
                       by.y = "stripped_cell_line_name", all.x = T)
# fwrite(gdsc_anno_leu2, file = "Output/Steps/R04/gdsc_anno_leu2.csv")

gdsc_anno_leu <- fread("Output/Steps/R04/gdsc_anno_leu2.csv")
```

```{r}
gdsc_anno_leu[gdsc_anno_leu$lineage_subtype %in% c("hairy_cell_leukaemia", "hairy_cell_leukemia"),]$lineage_subtype <- "HCL"

gdsc_anno_leu[gdsc_anno_leu$lineage_subtype %in% c("acute_biphenotypic_leukemia"),]$lineage_subtype <- "ABL"
```


# CCLE
## Cell anno
```{r}
ccle_anno_raw <- fread("Input/Datasets/CCLE/sample_info.csv")
ccle_anno <- ccle_anno_raw[,c(
  "DepMap_ID",
  "stripped_cell_line_name",
  "primary_disease",
  "Subtype",
  "lineage",
  "lineage_subtype",
  "lineage_sub_subtype",
  "lineage_molecular_subtype"
)]
```

```{r}
table(ccle_anno$primary_disease)
```


Select leukemia-related cell lines:
```{r}
ccle_anno_leu <- ccle_anno[ccle_anno$primary_disease %in% "Leukemia",]

table(ccle_anno_leu$Subtype)
```

```{r}
table(ccle_anno_leu$lineage_subtype)
```

```{r}
ccle_anno_leu[ccle_anno_leu$lineage_subtype %in% c("hairy_cell_leukemia"),]$lineage_subtype <- "HCL"

ccle_anno_leu[ccle_anno_leu$lineage_subtype %in% c("acute_biphenotypic_leukemia"),]$lineage_subtype <- "ABL"

ccle_anno_leu[ccle_anno_leu$lineage_subtype %in% c("unspecified_leukemia"),]$lineage_subtype <- "ALL"
```

## mRNA
```{r}
ccle_exp_raw <- fread("Input/Datasets/CCLE/CCLE_expression.csv")
ccle_exp <- as.data.frame(ccle_exp_raw)
rownames(ccle_exp) <- ccle_exp$V1; ccle_exp$V1 <- NULL
colnames(ccle_exp) <- gsub(" \\(\\d*.\\)", replacement = "", x = colnames(ccle_exp))
ccle_exp <- as.data.frame(t(ccle_exp))
```

Select leukemia-related cell lines:
```{r}
ccle_exp_leu <- ccle_exp[,colnames(ccle_exp) %in% ccle_anno_leu$DepMap_ID]
```

```{r}
ccle_anno_leu2 <- ccle_anno_leu[match(colnames(ccle_exp_leu), ccle_anno_leu$DepMap_ID),]
colnames(ccle_exp_leu) <- ccle_anno_leu2$stripped_cell_line_name
```

## fusion
```{r}
ccle_fusion <- fread("Input/Datasets/CCLE/CCLE_fusions.csv")
ccle_fusion_leu <- ccle_fusion[ccle_fusion$DepMap_ID %in% ccle_anno_leu$DepMap_ID,]
ccle_fusion_leu <- unique(ccle_fusion_leu[,1:2])
ccle_fusion_leu <- merge(ccle_fusion_leu,
                         ccle_anno_leu[,c(1:2)],
                         by = "DepMap_ID")
```

## miRNA
```{r}
ccle_miRNA <- fread("Input/Datasets/CCLE/CCLE_miRNA_20180525.gct")
ccle_miRNA <- as.data.frame(ccle_miRNA)
rownames(ccle_miRNA) <- ccle_miRNA$Description
ccle_miRNA <- ccle_miRNA[,-c(1:2)]
colnames(ccle_miRNA) <- gsub("_.*$", "", colnames(ccle_miRNA))
```

sel:
```{r}
ccle_miRNA_leu <- ccle_miRNA[,colnames(ccle_miRNA) %in% ccle_anno_leu$stripped_cell_line_name]
```

## Meth
```{r}
ccle_meth <- fread("Input/Datasets/CCLE/CCLE_RRBS_TSS_1kb_20180614.txt")
ccle_meth <- as.data.frame(ccle_meth)
rownames(ccle_meth) <- ccle_meth$TSS_id
ccle_meth <- ccle_meth[,-c(1:7)]
colnames(ccle_meth) <- gsub("_.*$", "", colnames(ccle_meth))
```

sel:
```{r}
ccle_meth_leu <- ccle_meth[,colnames(ccle_meth) %in% ccle_anno_leu$stripped_cell_line_name]
```

## Mut
```{r}
ccle_mut <- fread("Input/Datasets/CCLE/CCLE_mutations.csv")
ccle_mut_leu <- ccle_mut[ccle_mut$DepMap_ID %in% ccle_anno_leu$DepMap_ID,]

table(ccle_mut_leu$Variant_Classification)
```

## CNV
```{r}
ccle_cnv <- fread("Input/Datasets/CCLE/CCLE_copynumber_byGene_2013-12-03.txt")
ccle_cnv <- as.data.frame(ccle_cnv)
rownames(ccle_cnv) <- ccle_cnv$SYMBOL
ccle_cnv <- ccle_cnv[,-c(1:5)]
colnames(ccle_cnv) <- gsub("_.*$", "", colnames(ccle_cnv))

ccle_cnv_leu <- ccle_cnv[,colnames(ccle_cnv) %in% ccle_anno_leu$stripped_cell_line_name]
# tmp$ccle_anno_leu <- ccle_anno_leu[match(colnames(ccle_cnv_leu), ccle_anno_leu$DepMap_ID),]
# colnames(ccle_cnv_leu) <- tmp$ccle_anno_leu$stripped_cell_line_name
```

## Protein
```{r}
ccle_protein <- fread("Input/Datasets/CCLE/CCLE_RPPA_20180123.csv")
ccle_protein <- as.data.frame(ccle_protein)
rownames(ccle_protein) <- ccle_protein$V1; ccle_protein$V1 <- NULL
ccle_protein <- as.data.frame(t(ccle_protein))
colnames(ccle_protein) <- gsub("_.*$", "", colnames(ccle_protein))

ccle_protein_leu <- ccle_protein[,colnames(ccle_protein) %in% ccle_anno_leu$stripped_cell_line_name]
```

## Drugs
### PRISM1

### PRISM2
```{r}
# prism2_drug_raw <- fread("Input/Datasets/CCLE/secondary-screen-dose-response-curve-parameters.csv")
# prism2_drug <- prism2_drug_raw[,c("depmap_id", "name", "auc")]
# 
# prism2_drug <- dcast(data.table(prism2_drug), depmap_id~name,
#                  value.var="auc", fun.aggregate = max, fill = NA)
# prism2_drug <- prism2_drug[-1,]
# prism2_drug <- as.data.frame(prism2_drug)
```

Select leukemia:
```{r}
# prism2_drug_leu <- prism2_drug[prism2_drug$depmap_id %in% ccle_anno_leu$DepMap_ID,]
```

### CTRP1
```{r}
ctrp1_drug <- fread("Input/Datasets/CCLE/v10.D3.area_under_conc_curve.txt")

ctrp1_drug_leu <- unique(ctrp1_drug)
ctrp1_drug_leu <- merge(ctrp1_drug_leu,
                        ccle_anno_leu[,c(1,2)],
                        by.x = "ccl_name",
                        by.y = "stripped_cell_line_name")
ctrp1_drug_leu$ccl_name <- NULL

ctrp1_drug_leu <- dcast(data.table(ctrp1_drug_leu), DepMap_ID~cpd_name, value.var="area_under_curve", fun.aggregate = max, fill = NA)
```

### CTRP2
```{r}
ctrp2_drug <- fread("Input/Datasets/CCLE/v21.data.auc_sensitivities.txt") 
tmp$ctrp2_anno_ccl <- fread("Input/Datasets/CCLE/v21.meta.per_cell_line.txt") 
tmp$ctrp2_anno_cpd <- fread("Input/Datasets/CCLE/v21.meta.per_compound.txt") 

ctrp2_drug <- merge(ctrp2_drug, tmp$ctrp2_anno_ccl[,c(1,2)], by = "master_ccl_id")
ctrp2_drug <- merge(ctrp2_drug, tmp$ctrp2_anno_cpd[,c(1,2)], by = "master_cpd_id")
ctrp2_drug <- ctrp2_drug[,c(4,5,6)]
ctrp2_drug <- unique(ctrp2_drug)
ctrp2_drug_leu <- ctrp2_drug[ctrp2_drug$ccl_name %in% ccle_anno_leu$stripped_cell_line_name,]
ctrp2_drug_leu <- merge(ctrp2_drug_leu,
                        ccle_anno_leu[,c(1,2)],
                        by.x = "ccl_name",
                        by.y = "stripped_cell_line_name")
ctrp2_drug_leu$ccl_name <- NULL

ctrp2_drug_leu <- dcast(data.table(ctrp2_drug_leu), DepMap_ID~cpd_name, value.var="area_under_curve", fun.aggregate = max, fill = NA)
```

```{r}
ctrp1_drug_leu <- changeName(df1 = ctrp1_drug_leu,
                              df2 = ccle_anno_leu,
                              col1 = "DepMap_ID",
                              col2 = "stripped_cell_line_name")

ctrp2_drug_leu <- changeName(df1 = ctrp2_drug_leu,
                              df2 = ccle_anno_leu,
                              col1 = "DepMap_ID",
                              col2 = "stripped_cell_line_name")
```


# BeatAML
```{r}
availablePSets <- availablePSets()
```

```{r}
# beatAML <- downloadPSet("BeatAML_2018")
# 
# saveRDS(beatAML, file = "Input/Datasets/BeatAML/BeatAML_2018.rds")
```

```{r}
beatAML <- readRDS("Input/Datasets/BeatAML/BeatAML_2018.rds")
```

## anno
```{r}
beatAML_anno_leu <- beatAML@sample

# Drug anno
beatAML_druganno_leu <- beatAML@treatment
```

## mRNA
```{r}
beatAML_exp_leu <- as.data.frame(assay(beatAML@molecularProfiles$rnaseq.counts))
beatAML_exp_leu$genes <- rownames(beatAML_exp_leu)
beatAML_exp_leu$genes <- substr(beatAML_exp_leu$genes, 1, 15)

genecode <- fread("Input/gencode.v22.annotation.gene.probeMap")
genecode$id <- substr(genecode$id, 1, 15)
beatAML_exp_leu <- merge(beatAML_exp_leu,
                  genecode[,-c(3:6)],
                  by.x = "genes",
                  by.y = "id")
beatAML_exp_leu$genes <- NULL
beatAML_exp_leu <- aggregate(.~gene, 
                             max, 
                             data = beatAML_exp_leu)
rownames(beatAML_exp_leu) <- beatAML_exp_leu$gene
beatAML_exp_leu$gene <- NULL
```

## Mut
```{r}
beatAML_mut_leu <- as.data.frame(assay(beatAML@molecularProfiles$mutationall))
beatAML_mut_leu$genes <- rownames(beatAML_mut_leu)

beatAML_mut_leu <- gather(data = beatAML_mut_leu,
                     key = cells,
                     value = mutation,
                     - genes)
beatAML_mut_leu <- beatAML_mut_leu[!beatAML_mut_leu$mutation %in% "wt",]

```

## drugs
```{r}
beatAML_drug_leu <- beatAML@treatmentResponse$profiles
beatAML_drug_leu$drug_names <- rownames(beatAML_drug_leu)
beatAML_drug_leu$drug_names <- gsub("drugid.", "", beatAML_drug_leu$drug_names)
beatAML_drug_leu$drug_names <- gsub("\\.Full\\d\\.\\d\\.\\d\\.\\d+$", "", beatAML_drug_leu$drug_names)
beatAML_drug_leu$drug_names <- gsub(".", ":", beatAML_drug_leu$drug_names, fixed = T)
beatAML_drug_leu <- separate(beatAML_drug_leu, col = drug_names, into = c("drug", "cell"),sep = ":")

beatAML_drug_leu <- dcast(data.table(beatAML_drug_leu), cell~drug,
                        value.var="aac_recomputed", fun.aggregate = max, fill = NA)
```

# Tavor
```{r}
# tavor <- downloadPSet("Tavor_2020")
# saveRDS(tavor, file = "Input/Datasets/Tavor/Tavor_2020.rds")

tavor <- readRDS("Input/Datasets/Tavor/Tavor_2020.rds")
```

## anno
```{r}
# anno
tavor_anno <- tavor@sample
tavor_anno_leu <- tavor_anno[!tavor_anno$Diagnosis %in% NA,]

# Drug anno
tavor_druganno_leu <- tavor@treatment
```

## mRNA
```{r}
tavor_exp <- as.data.frame(assay(tavor@molecularProfiles$rnaseq))
tavor_exp <- as.data.frame(log2(tavor_exp + 1))
tavor_exp_leu <- tavor_exp[,colnames(tavor_exp) %in% tavor_anno_leu$sampleid]
```

## drugs
```{r}
tavor_drug_leu <- tavor@treatmentResponse$profiles
tavor_drug_leu$Molecule.Name <- substr(rownames(tavor_drug_leu),
                                       1, 11)
tavor_drug_leu$cell <- substr(
  rownames(tavor_drug_leu),
  15, 20
)

tavor_drug_leu <- merge(tavor_drug_leu,
                        tavor_druganno_leu[,c(1,4)],
                        by = "Molecule.Name")
tavor_drug_leu <- tavor_drug_leu[!tavor_drug_leu$ic50_recomputed %in% Inf,]
tavor_drug_leu <- dcast(data.table(tavor_drug_leu), cell~treatmentid,
                        value.var="ic50_recomputed", fun.aggregate = max, fill = NA)
tavor_drug_leu <- tavor_drug_leu[tavor_drug_leu$cell %in% tavor_anno_leu$sampleid,]
```


# gCSI
```{r}
# gCSI <- downloadPSet("gCSI_2019", timeout = 10000)
# saveRDS(gCSI, file = "Input/Datasets/GCSI/gCSI_2019.Rds")

gCSI <- readRDS("Input/Datasets/GCSI/gCSI_2019.Rds")
```

## anno
```{r}
# table(gCSI_anno_leu$sampleid %in% ccle_anno_leu$stripped_cell_line_name)
# 
# gCSI_anno_leu$sampleid[!gCSI_anno_leu$sampleid %in% ccle_anno_leu$stripped_cell_line_name]
```

```{r}
gCSI_anno <- gCSI@sample
gCSI_anno_leu <- gCSI_anno[grepl("leukemia", gCSI_anno$Cellosaurus.Disease.Type),]

gCSI_anno_leu$old_name <- rownames(gCSI_anno_leu)
tmp$gCSI_anno_leu <- gCSI_anno_leu
gCSI_anno_leu$sampleid <- gsub(
  "-", "", gCSI_anno_leu$sampleid
)
gCSI_anno_leu$sampleid <- gsub(
  ";", "", gCSI_anno_leu$sampleid
)
gCSI_anno_leu$sampleid <- gsub(
  " [Human leukemia]", "", gCSI_anno_leu$sampleid, fixed = T
)
gCSI_anno_leu$sampleid <- toupper(gCSI_anno_leu$sampleid)

gCSI_anno_leu <- ccle_anno_leu[match(gCSI_anno_leu$sampleid,
                                     ccle_anno_leu$stripped_cell_line_name),]
gCSI_anno_leu[13,] <- list("ACH-000157",
                        "A4/FUKUDA",
                        "Leukemia",
                        "Non-Hodgkin Lymphoma",
                        "blood",
                        "NHL",
                        "b_cell",
                        NA)
gCSI_anno_leu[14,] <- list("CVCL_1860",
                        "CCRFSB",
                        "Leukemia",
                        "Acute lymphoblastic leukemia",
                        "blood",
                        "ALL",
                        "b_cell",
                        NA)
gCSI_anno_leu[17,] <- list("ACH-000995",
                        "JURKAT",
                        "Leukemia",
                        "Acute Lymphoblastic Leukemia (ALL), T-cell",
                        "blood",
                        "ALL",
                        "t_cell",
                        NA)

gCSI_anno_leu$old_names <- tmp$gCSI_anno_leu$old_name


```

```{r}
# Drug anno
gCSI_druganno_leu <- gCSI@treatment
```

## mRNA
```{r}
# gCSI_exp <- as.data.frame(assay(gCSI@molecularProfiles$Kallisto_0.46.1.rnaseq.counts))
# tavor_exp <- as.data.frame(log2(tavor_exp + 1))
# tavor_exp_leu <- tavor_exp[,colnames(tavor_exp) %in% tavor_anno_leu$sampleid]
```

## CNV
```{r}
gCSI_cnv <- as.data.frame(assay(gCSI@molecularProfiles$cnv))
gCSI_cnv_leu <- gCSI_cnv[,colnames(gCSI_cnv) %in% gCSI_anno_leu$old_names]
```

## Mut
```{r}
gCSI_mut <- as.data.frame(assay(gCSI@molecularProfiles$mutation))
gCSI_mut_leu <- gCSI_mut[,colnames(gCSI_mut) %in% gCSI_anno_leu$old_names]

gCSI_mut_leu$genes <- rownames(gCSI_mut_leu)

gCSI_mut_leu <- gather(data = gCSI_mut_leu,
                     key = cells,
                     value = mutation,
                     - genes)
gCSI_mut_leu <- gCSI_mut_leu[!gCSI_mut_leu$mutation %in% "wt",]
gCSI_mut_leu <- gCSI_mut_leu[!is.na(gCSI_mut_leu$mutation),]
```


## drugs
```{r}
gCSI_drug <- gCSI@treatmentResponse$profiles
gCSI_drug$label <- rownames(gCSI_drug)
gCSI_drug <- separate(gCSI_drug, col = "label", into = c("cells", "drugs", "others"), sep = "_")
gCSI_drug_leu <- gCSI_drug[gCSI_drug$cells %in% gCSI_anno_leu$old_names,]

gCSI_drug_leu <- dcast(data.table(gCSI_drug_leu), cells~drugs,
                        value.var="ic50_recomputed", fun.aggregate = max, fill = NA)
```

# FORALL
## anno
```{r}
FORALL_anno <- read_xlsx("Input/Datasets/FORALL/cellanno.xlsx", sheet = 2)

FORALL_anno_leu <- cbind.data.frame(
  names = FORALL_anno$`Cell Line Name`,
  types = "ALL"
)

# druganno
FORALL_druganno_leu <- read_xlsx("Input/Datasets/FORALL/druganno.xlsx", sheet = 2)
```

## Fusion
```{r}
FORALL_fusion_leu <- as.data.frame(read_xlsx("Input/Datasets/FORALL/fusion.xlsx", sheet = 2))
FORALL_fusion_leu <- FORALL_fusion_leu[-c(1:2),]
```

## Protein
```{r}
FORALL_protein_leu <- as.data.frame(read_xlsx("Input/Datasets/FORALL/protein.xlsx", sheet = 2))
rownames(FORALL_protein_leu) <- FORALL_protein_leu$...1
FORALL_protein_leu$...1 <- NULL
```

## Mut
```{r}
FORALL_mut_leu <- as.data.frame(fread("Input/Datasets/FORALL/mut.txt"))
```

## drugs
```{r}
FORALL_drug <- read_xlsx("Input/Datasets/FORALL/drugs.xlsx", sheet = 2)
FORALL_drug_leu <- as.data.frame(FORALL_drug)
rownames(FORALL_drug_leu) <- FORALL_drug_leu$...1
FORALL_drug_leu$...1 <- NULL
FORALL_drug_leu <- as.data.frame(t(FORALL_drug_leu))
FORALL_drug_leu <- cbind.data.frame(cells = rownames(FORALL_drug_leu), FORALL_drug_leu)
```

# Drug Anno(GDSC)
This steps were processed after R02.

```{r}
# drug_anno <- fread("Input/Datasets/Drug/Repurposing_Hub_export.txt")
```

## GDSC
```{r}
gdsc_drug_anno <- fread("Input/Datasets/Drug/gdsc_screened_compounds_rel_8.4.csv")
gdsc_drug_anno$DRUG_ID <- NULL;gdsc_drug_anno$SCREENING_SITE <- NULL
gdsc_drug_anno$DRUG_NAME2 <- toupper(gdsc_drug_anno$DRUG_NAME)

gdsc_drug_anno <- unique(gdsc_drug_anno)
```

```{r}
table(colnames(gdsc1_drug_leu2[-1]) %in% gdsc_drug_anno$DRUG_NAME2)

table(colnames(gdsc2_drug_leu2[-1]) %in% gdsc_drug_anno$DRUG_NAME2)
```

```{r}
head(colnames(gdsc1_drug_leu2[-1])[!colnames(gdsc1_drug_leu2[-1]) %in% gdsc_drug_anno$DRUG_NAME2], 3)
```

### Handle diff drug names
gdsc:
```{r}
drug <- unique(c(colnames(gdsc1_drug_leu2[-1]),
                 colnames(gdsc2_drug_leu2[-1])))

drug1 <- drug[drug %in% gdsc_drug_anno$DRUG_NAME2]
drug2 <- drug[!drug %in% gdsc_drug_anno$DRUG_NAME2]
```

```{r}
drug2 <- data.frame(name = drug2,
                    name1 = drug2)
drug2 <- separate(drug2,col = name1, into = c("name1", "name2"),sep = ",")
head(drug2)
```

```{r}
table(drug2$name1 %in% gdsc_drug_anno$DRUG_NAME2)
table(drug2$name2 %in% gdsc_drug_anno$DRUG_NAME2)
```

```{r}
drug3 <- drug2[drug2$name1 %in% gdsc_drug_anno$DRUG_NAME2,]
drug4 <- drug2[!drug2$name1 %in% gdsc_drug_anno$DRUG_NAME2,]
```

```{r}
gdsc_drug_anno2 <- gdsc_drug_anno[,c(5,2)]
```

```{r}
index <- sapply(drug4$name1, function(x){
  which(grepl(x, gdsc_drug_anno2$SYNONYMS))
})
index <- index[!sapply(index, is_empty)]
drug5 <- data.frame(index = unlist(index),
                    name1 = names(index),
                    old = drug4$name[drug4$name1 %in% names(index)])
# index$V2 <- rownames(index)
drug5$new <- gdsc_drug_anno2[drug5$index,]$DRUG_NAME2
```

```{r}
drug6 <- drug4[!drug4$name %in% drug5$old,]
drug6$new <- gsub("-", "", drug6$name1)
```

```{r}
drug7 <- drug6[drug6$new %in% gdsc_drug_anno2$DRUG_NAME,]
drug8 <- drug6[!drug6$new %in% gdsc_drug_anno2$DRUG_NAME,]
```

### Rename
```{r}
gdsc_drug_rename <- data.frame(
  old = drug,
  new = drug
)

# 1st
identical(gdsc_drug_rename$new[gdsc_drug_rename$new %in% drug3$name],
          drug3$name)
gdsc_drug_rename$new[gdsc_drug_rename$new %in% drug3$name] <- drug3$name1
```

```{r}
# 2ed
identical(gdsc_drug_rename$new[gdsc_drug_rename$new %in% drug5$old],
          drug5$old)
gdsc_drug_rename$new[gdsc_drug_rename$new %in% drug5$old] <- drug5$new

# 3rd
gdsc_drug_rename$new[gdsc_drug_rename$new %in% drug7$name] <- drug7$new
```

### Reprocess anno files
```{r}
gdsc_drug_anno_split1 <- gdsc_drug_anno[gdsc_drug_anno$DRUG_NAME2 %in% gdsc_drug_rename$new,]
gdsc_drug_anno_split1$DRUG_NAME <- NULL
```

```{r}
table(gdsc_drug_rename$new %in% gdsc_drug_anno_split1$DRUG_NAME2)
```

```{r}
gdsc_drug_anno_split2 <- data.frame(
  DRUG_NAME2 = drug8$name
)
gdsc_drug_anno_split2$TARGET_PATHWAY <- c("Cell cycle",
                                          "RTK signaling",
                                          "EGFR signaling",
                                          "EGFR signaling",
                                          "mitosis",
                                          "Other, kinases",
                                          "RTK signaling",
                                          "Apoptosis regulation",
                                          "Cell cycle",
                                          "hedgehog pathway",
                                          "PI3K/MTOR signaling",
                                          "Chromatin histone acetylation",
                                          "Chromatin other",
                                          "DNA replication",
                                          "IGF1R signaling",
                                          "Mitosis")
gdsc_drug_anno_split1$SYNONYMS <- NULL
gdsc_drug_anno_split1$TARGET <- NULL
```

```{r}
gdsc_drug_anno <- rbind(gdsc_drug_anno_split2,
                        gdsc_drug_anno_split1[,c(2,1)])
```

```{r}
table(gdsc_drug_rename$new %in% gdsc_drug_anno$DRUG_NAME2)
```

```{r}
gdsc_drug_anno <- unique(gdsc_drug_anno)
dupli <- gdsc_drug_anno[gdsc_drug_anno$DRUG_NAME2 %in% gdsc_drug_anno$DRUG_NAME2[duplicated(gdsc_drug_anno$DRUG_NAME2)],]
```

# Rescale data
```{r}
source("Function.R")
```


```{r}
# GDSC
# load(file = "Output/Steps/R01/gdsc_drug_leu_v1.Rda")
gdsc1_drug_leu <- rescaleMode1(gdsc1_drug_leu)
gdsc2_drug_leu <- rescaleMode1(gdsc2_drug_leu)

# CTRP
# load(file = "Output/Steps/R01/ccle_drug_leu_v1.Rda")
ctrp1_drug_leu <- rescaleMode1(ctrp1_drug_leu)
ctrp2_drug_leu <- rescaleMode1(ctrp2_drug_leu)

# Tavor
# load(file = "Output/Steps/R01/tavor_drug_leu_v1.Rda")
tavor_drug_leu <- rescaleMode1(tavor_drug_leu)

# gCSI
# load(file = "Output/Steps/R01/gCSI_drug_leu_v1.Rda")
gCSI_drug_leu <- rescaleMode1(gCSI_drug_leu)
```

# Drug preprocess
```{r}
drugRename <- function(df){
  # df <- ctrp1_drug_leu
  rownames(df) <- df[,1]
  df[,1] <- NULL
  return(df)
}
ctrp1_drug <- drugRename(ctrp1_drug_leu)
ctrp2_drug <- drugRename(ctrp2_drug_leu)
gdsc1_drug <- drugRename(gdsc1_drug_leu)
gdsc2_drug <- drugRename(gdsc2_drug_leu)
FORALL_drug <- drugRename(FORALL_drug_leu)
gCSI_drug <- as.data.frame(drugRename(gCSI_drug_leu))
beatAML_drug <- drugRename(as.data.frame(beatAML_drug_leu))
tavor_drug <- drugRename(tavor_drug_leu)
```

# Save
## GDSC
```{r}
# save(
#   gdsc_exp_leu,
#   gdsc_anno_leu,
#   gdsc1_drug_leu,
#   gdsc2_drug_leu,
#   gdsc_drug_anno,
#   file = "Output/Steps/R01/gdsc_leu_v2.Rda")

# exp
save(
  gdsc_exp_leu,
  gdsc_anno_leu,
  file = "Output/Steps/R01/gdsc_exp_leu_v1.Rda"
)

# fusion
save(
  gdsc_fusion_leu,
  gdsc_anno_leu,
  file = "Output/Steps/R01/gdsc_fusion_leu_v1.Rda"
)

# mut
save(
  gdsc_mut_leu,
  gdsc_anno_leu,
  file = "Output/Steps/R01/gdsc_mut_leu_v1.Rda"
)

# cnv
save(
  gdsc_cnv_leu,
  gdsc_anno_leu,
  file = "Output/Steps/R01/gdsc_cnv_leu_v1.Rda"
)

# drug
save(
  gdsc1_drug_leu,
  gdsc2_drug_leu,
  gdsc_drug_anno,
  gdsc_anno_leu,
  file = "Output/Steps/R01/gdsc_drug_leu_v1.Rda"
)
```

## CCLE
```{r}
# save(
#   ccle_exp_leu,
#   ccle_anno_leu,
#   ctrp1_drug_leu,
#   ctrp2_drug_leu,
#   file = "Output/Steps/R01/ccle_leu_v1.Rda")

# exp
save(
  ccle_exp_leu,
  ccle_anno_leu,
  file = "Output/Steps/R01/ccle_exp_leu_v1.Rda"
)

# meth
save(
  ccle_meth_leu,
  ccle_anno_leu,
  file = "Output/Steps/R01/ccle_meth_leu_v1.Rda"
)

# miRNA
save(
  ccle_miRNA_leu,
  ccle_anno_leu,
  file = "Output/Steps/R01/ccle_miRNA_leu_v1.Rda"
)

# fusion
save(
  ccle_fusion_leu,
  ccle_anno_leu,
  file = "Output/Steps/R01/ccle_fusion_leu_v1.Rda"
)

# mut
save(
  ccle_mut_leu,
  ccle_anno_leu,
  file = "Output/Steps/R01/ccle_mut_leu_v1.Rda"
)

# cnv
save(
  ccle_cnv_leu,
  ccle_anno_leu,
  file = "Output/Steps/R01/ccle_cnv_leu_v1.Rda"
)

# protein
save(
  ccle_protein_leu,
  ccle_anno_leu,
  file = "Output/Steps/R01/ccle_protein_leu_v1.Rda"
)

# drug
save(
  ctrp1_drug_leu,
  ctrp2_drug_leu,
  ccle_anno_leu,
  file = "Output/Steps/R01/ccle_drug_leu_v1.Rda"
)
```

GDSC Drug anno:
```{r}
save(gdsc_drug_anno,
     gdsc_drug_rename,
     file = "Output/Steps/R01/gdsc_drug_anno_v2.Rda")
```

## beatAML
```{r}
# exp
save(
  beatAML_exp_leu,
  beatAML_anno_leu,
  file = "Output/Steps/R01/beatAML_exp_leu_v1.Rda"
)

# mut
save(
  beatAML_mut_leu,
  beatAML_anno_leu,
  file = "Output/Steps/R01/beatAML_mut_leu_v1.Rda"
)

# drug
save(
  beatAML_drug_leu,
  beatAML_anno_leu,
  file = "Output/Steps/R01/beatAML_drug_leu_v1.Rda"
)
```

## Tavor
```{r}
# exp
save(
  tavor_exp_leu,
  tavor_anno_leu,
  file = "Output/Steps/R01/tavor_exp_leu_v1.Rda"
)

# drug
save(
  tavor_drug_leu,
  tavor_anno_leu,
  file = "Output/Steps/R01/tavor_drug_leu_v1.Rda"
)
```

## gCSI
```{r}
# cnv
save(
  gCSI_cnv_leu,
  gCSI_anno_leu,
  file = "Output/Steps/R01/gCSI_cnv_leu_v1.Rda"
)

# mut
save(
  gCSI_mut_leu,
  gCSI_anno_leu,
  file = "Output/Steps/R01/gCSI_mut_leu_v1.Rda"
)

# drug
save(
  gCSI_drug_leu,
  gCSI_anno_leu,
  file = "Output/Steps/R01/gCSI_drug_leu_v1.Rda"
)
```

## FORALL
```{r}
# fusion
save(
  FORALL_fusion_leu,
  FORALL_anno_leu,
  file = "Output/Steps/R01/FORALL_fusion_leu_v1.Rda"
)

# mut
save(
  FORALL_mut_leu,
  FORALL_anno_leu,
  file = "Output/Steps/R01/FORALL_mut_leu_v1.Rda"
)

# protein
save(
  FORALL_protein_leu,
  FORALL_anno_leu,
  file = "Output/Steps/R01/FORALL_protein_leu_v1.Rda"
)

# drug
save(
  FORALL_drug_leu,
  FORALL_druganno_leu,
  FORALL_anno_leu,
  file = "Output/Steps/R01/FORALL_drug_leu_v1.Rda"
)
```

## Drugs
```{r}
save(
  ctrp1_drug,
  ctrp2_drug,
  gdsc1_drug,
  gdsc2_drug,
  FORALL_drug,
  gCSI_drug,
  beatAML_drug,
  tavor_drug, file = "Output/Steps/R01/shiny/merged_drug_df.Rda"
)
```

## Annos
```{r}
save(
  ctrp1_drug
)
```

