```{r library, include=FALSE}
my_packages <- c("tidyverse", "data.table", 
                 "plyr", "withr",
                 "ggpubr", "patchwork", "plotly",
                 "umap", "Rtsne", "FactoMineR", "factoextra",
                 "impute")
pacman::p_load(char = my_packages)

tmp <- list()
```

```{r}
source("Function.R")
```


# load data
```{r}
load("Output/Steps/R01/ccle_drug_leu_v1.Rda")

load("Output/Steps/R01/gdsc_drug_leu_v1.Rda")

load(file = "Output/Steps/R01/beatAML_drug_leu_v1.Rda")

load(file = "Output/Steps/R01/tavor_drug_leu_v1.Rda")

load(file = "Output/Steps/R01/gCSI_drug_leu_v1.Rda")

load(file = "Output/Steps/R01/FORALL_drug_leu_v1.Rda")
```

```{r}
load("Output/Steps/R01/gdsc_drug_anno_v2.Rda")
```

```{r}
drug_anno <- fread("Input/Datasets/Drug/Repurposing_Hub_export.txt")
```

# Preprocess
```{r}
ctrp1 <- ctrp1_drug_leu

ctrp2 <- ctrp2_drug_leu

gdsc1 <- gdsc1_drug_leu

gdsc2 <- gdsc2_drug_leu

beatAML <- beatAML_drug_leu

gCSI <- gCSI_drug_leu

tavor <- tavor_drug_leu

FORALL <- FORALL_drug_leu
```

# Overall pharmaceutics(sd and median)
## gdsc1
```{r}
gdsc_overall <- calSDandMedian(gdsc1)
gdsc_overall$Drugs <- rownames(gdsc_overall)
gdsc_overall <- merge(gdsc_overall,
                      gdsc_drug_rename,
                      by.x = "Drugs",
                      by.y = "old")
gdsc_overall <- merge(gdsc_overall,
                      gdsc_drug_anno,
                      by.x = "new",
                      by.y = "DRUG_NAME2")
tmp$dupli <- gdsc_overall$new[duplicated(gdsc_overall$new)]
tmp$dupli
```

```{r}
gdsc_overall <- gdsc_overall[-c(29,31),]
gdsc_overall[30,]$TARGET_PATHWAY <- "IGF1R/RTK signaling"
```

```{r}
gdsc1_overall <- gdsc_overall
```


```{r}
p <- ggplot(data = gdsc1_overall, 
            aes(x = SD, 
                y = Median, label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=TARGET_PATHWAY)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("ggsci::default_igv"))
p
```

```{r}
for_label_med <- gdsc_overall[order(gdsc_overall$Median),] %>% 
  head(10)
```


```{r}
p_gdsc1 <- p +
  geom_point(size = 3, shape = 1, data = for_label_med) +
  ggrepel::geom_label_repel(
    aes(label = Drugs),
    data = for_label_med,
    color="black"
  )
p_gdsc1
```

```{r}
p_sd_gdsc1 <- p
```


## gdsc2
```{r}
gdsc_overall <- calSDandMedian(gdsc2)
gdsc_overall$Drugs <- rownames(gdsc_overall)
gdsc_overall <- merge(gdsc_overall,
                      gdsc_drug_rename,
                      by.x = "Drugs",
                      by.y = "old")
gdsc_overall <- merge(gdsc_overall,
                      gdsc_drug_anno,
                      by.x = "new",
                      by.y = "DRUG_NAME2")
tmp$dupli <- gdsc_overall$new[duplicated(gdsc_overall$new)]
tmp$dupli
```

```{r}
gdsc_overall <- gdsc_overall[-c(15,20,31,45,51,86),]
gdsc_overall$TARGET_PATHWAY[gdsc_overall$Drugs %in% c("DASATINIB",
                                                      "GSK1904529A",
                                                      "LAPATINIB",
                                                      "SORAFENIB")] <- 
  c("kinases & RTK signaling",
    "IGF1R/RTK signaling",
    "EGFR/RTK signaling",
    "kinases & RTK signaling")
```

```{r}
gdsc2_overall <- gdsc_overall
```


```{r}
p <- ggplot(data = gdsc2_overall, 
            aes(x = SD, 
                y = Median,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=TARGET_PATHWAY)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("ggsci::default_igv"))
p
```

```{r}
for_label_med <- gdsc_overall[order(gdsc_overall$Median),] %>% 
  head(10)

# for_label_sd <- gdsc_overall[order(gdsc_overall$SD, decreasing = T),] %>% 
#   head(3)

# for_label <- unique(rbind(for_label_med, for_label_sd))
```


```{r}
p_gdsc2 <- p +
  geom_point(size = 3, shape = 1, data = for_label_med) +
  ggrepel::geom_label_repel(
    aes(label = Drugs),
    data = for_label_med,
    color="black"
  )
p_gdsc2
```

```{r}
p_sd_gdsc2 <- p
```

```{r}
# p_gdsc <- p_gdsc1 + p_gdsc2
# p_gdsc
```

## ctrp1
```{r}
ctrp_overall <- calSDandMedian(ctrp1)
ctrp_overall$Drugs <- rownames(ctrp_overall)
```

```{r}
table(ctrp_overall$Drugs %in% drug_anno$Name)
```
```{r}
ctrp_overall1 <- merge(ctrp_overall,
                       drug_anno[,1:2], by.x = "Drugs",
                       by.y = "Name")
ctrp_overall2 <- ctrp_overall[!ctrp_overall$Drugs %in% drug_anno$Name,]
ctrp_overall2$MOA <- "Unknown"

ctrp1_overall <- rbind(ctrp_overall1,
                       ctrp_overall2)
```

```{r}
p <- ggplot(data = ctrp1_overall, 
            aes(x = SD, 
                y = Median,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=MOA)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("palettesForR::Web")) + theme(legend.position = "none")
p
```

```{r}
for_label_med <- ctrp1_overall[order(ctrp1_overall$Median),] %>% 
  head(10)

# for_label_sd <- gdsc_overall[order(gdsc_overall$SD, decreasing = T),] %>% 
#   head(3)

# for_label <- unique(rbind(for_label_med, for_label_sd))
```


```{r}
p_ctrp1 <- p +
  geom_point(size = 3, shape = 1, data = for_label_med) +
  ggrepel::geom_label_repel(
    aes(label = Drugs),
    data = for_label_med,
    color="black",
    max.overlaps = Inf,
    min.segment.length = 0
  )
p_ctrp1
```

```{r}
p_sd_ctrp1 <- p
```

```{r}
plotly::ggplotly(p_sd_ctrp1)
```

## ctrp2
```{r}
ctrp_overall <- calSDandMedian(ctrp2)
ctrp_overall$Drugs <- rownames(ctrp_overall)
```

```{r}
table(ctrp_overall$Drugs %in% drug_anno$Name)
```
```{r}
ctrp_overall1 <- merge(ctrp_overall,
                       drug_anno[,1:2], by.x = "Drugs",
                       by.y = "Name")
ctrp_overall2 <- ctrp_overall[!ctrp_overall$Drugs %in% drug_anno$Name,]
ctrp_overall2$MOA <- "Unknown"

ctrp2_overall <- rbind(ctrp_overall1,
                       ctrp_overall2)
```

```{r}
p <- ggplot(data = ctrp2_overall, 
            aes(x = SD, 
                y = Median,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=MOA)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("palettesForR::Web")) + theme(legend.position = "none")
p
```

```{r}
for_label_med <- ctrp2_overall[order(ctrp2_overall$Median),] %>% 
  head(10)

# for_label_sd <- gdsc_overall[order(gdsc_overall$SD, decreasing = T),] %>% 
#   head(3)

# for_label <- unique(rbind(for_label_med, for_label_sd))
```


```{r}
p_ctrp2 <- p +
  geom_point(size = 3, shape = 1, data = for_label_med) +
  ggrepel::geom_label_repel(
    aes(label = Drugs),
    data = for_label_med,
    color="black",
    max.overlaps = Inf,
    min.segment.length = 0
  )
p_ctrp2
```

```{r}
p_sd_ctrp2 <- p
```

## gCSI
```{r}
gCSI_overall <- calSDandMedian(gCSI)
gCSI_overall$Drugs <- rownames(gCSI_overall)
gCSI_overall <- na.omit(gCSI_overall)
```

```{r}
gCSI_overall1 <- merge(gCSI_overall,
                       drug_anno[,1:2], by.x = "Drugs",
                       by.y = "Name")
gCSI_overall2 <- gCSI_overall[!gCSI_overall$Drugs %in% drug_anno$Name,]
gCSI_overall2$MOA <- "Unknown"

gCSI_overall <- rbind(gCSI_overall1,
                       gCSI_overall2)
```

```{r}
p <- ggplot(data = gCSI_overall, 
            aes(x = SD, 
                y = Median,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=MOA)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("palettesForR::Web")) + theme(legend.position = "none")
p_sd_gCSI <- p
p_sd_gCSI
```

## tavor
```{r}
tavor_overall <- calSDandMedian(tavor)
tavor_overall$Drugs <- rownames(tavor_overall)
tavor_overall <- na.omit(tavor_overall)
```

```{r}
tavor_overall1 <- merge(tavor_overall,
                       drug_anno[,1:2], by.x = "Drugs",
                       by.y = "Name")
tavor_overall2 <- tavor_overall[!tavor_overall$Drugs %in% drug_anno$Name,]
tavor_overall2$MOA <- "Unknown"

tavor_overall <- rbind(tavor_overall1,
                       tavor_overall2)
```

```{r}
p <- ggplot(data = tavor_overall, 
            aes(x = SD, 
                y = Median,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=MOA)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("palettesForR::Web")) + theme(legend.position = "none")
p_sd_tavor <- p
p_sd_tavor
```

## BeatAML
```{r}
BeatAML_overall <- calSDandMedian(beatAML)
BeatAML_overall$Drugs <- rownames(BeatAML_overall)
BeatAML_overall <- na.omit(BeatAML_overall)
```

```{r}
BeatAML_overall1 <- merge(BeatAML_overall,
                       drug_anno[,1:2], by.x = "Drugs",
                       by.y = "Name")
BeatAML_overall2 <- BeatAML_overall[!BeatAML_overall$Drugs %in% drug_anno$Name,]
BeatAML_overall2$MOA <- "Unknown"

BeatAML_overall <- rbind(BeatAML_overall1,
                       BeatAML_overall2)
```

```{r}
p <- ggplot(data = BeatAML_overall, 
            aes(x = SD, 
                y = Median,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=MOA)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("palettesForR::Web")) + theme(legend.position = "none")
p_sd_BeatAML <- p
p_sd_BeatAML
```

## FORALL
```{r}
FORALL_overall <- calSDandMedian(FORALL)
FORALL_overall$Drugs <- rownames(FORALL_overall)
FORALL_overall <- na.omit(FORALL_overall)
```

```{r}
FORALL_overall <- merge(FORALL_overall,
                       FORALL_druganno_leu[,c(1,4)], by.x = "Drugs",
                       by.y = "Drug name")
```

```{r}
p <- ggplot(data = FORALL_overall, 
            aes(x = SD, 
                y = Median,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=`Drug Class`)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("ggsci::default_igv")) 
p_sd_FORALL <- p
p_sd_FORALL
```

# Overall pharmaceutics(TSNE)
Select drugs with less than 20% missing data:
```{r}
ctrp1 <- ctrp1_drug_leu[,apply(ctrp1_drug_leu,2,function(x) sum(is.na(x))) < 0.2*nrow(ctrp1_drug_leu)]

ctrp2 <- ctrp2_drug_leu[,apply(ctrp2_drug_leu,2,function(x) sum(is.na(x))) < 0.2*nrow(ctrp2_drug_leu)]
# ctrp2 <- ctrp2_1[,apply(ctrp2_drug_leu2,2,function(x) sum(is.na(x))) < 0.2*nrow(ctrp2_drug_leu2)]

gdsc1 <- gdsc1_drug_leu[,apply(gdsc1_drug_leu,2,function(x) sum(is.na(x))) < 0.2*nrow(gdsc1_drug_leu)]

gdsc2 <- gdsc2_drug_leu[,apply(gdsc2_drug_leu,2,function(x) sum(is.na(x))) < 0.2*nrow(gdsc2_drug_leu)]

filterDrugDf <- function(x){
  x[,apply(x,2,function(x1) sum(is.na(x1))) < 0.2*nrow(x)]
  return(x)
}

beatAML <- beatAML_drug_leu[,apply(beatAML_drug_leu,2,function(x) sum(is.na(x))) < 0.2*nrow(beatAML_drug_leu)]

tavor <- tavor_drug_leu[,apply(tavor_drug_leu,2,function(x) sum(is.na(x))) < 0.2*nrow(tavor_drug_leu)]

FORALL <- FORALL_drug_leu[,apply(FORALL_drug_leu,2,function(x) sum(is.na(x))) < 0.2*nrow(FORALL_drug_leu)]

gCSI <- gCSI_drug_leu[,apply(gCSI_drug_leu,2,function(x) sum(is.na(x))) < 0.5*nrow(gCSI_drug_leu)]
```

## Preprocess(impute)
sample in the col(drugs)

```{r}
gdsc1_1 <- gdsc1
rownames(gdsc1_1) <- gdsc1$cell
gdsc1_1$cell <- NULL
gdsc1_1 <- as.data.frame(gdsc1_1)
```

impute missing data:
```{r}
gdsc1_1 <- impute.knn(as.matrix(gdsc1_1))$data
```

```{r}
gdsc2_1 <- gdsc2
rownames(gdsc2_1) <- gdsc2_1$cell
gdsc2_1$cell <- NULL
gdsc2_1 <- as.data.frame(gdsc2_1)
```

impute missing data:
```{r}
gdsc2_1 <- impute.knn(as.matrix(gdsc2_1))$data
```

```{r}
ctrp1_1 <- ctrp1
rownames(ctrp1_1) <- ctrp1_1$cell 
ctrp1_1$cell <- NULL
ctrp1_1 <- as.data.frame(ctrp1_1)

ctrp1_1 <- impute.knn(as.matrix(ctrp1_1))$data
```

```{r}
ctrp2_1 <- ctrp2
rownames(ctrp2_1) <- ctrp2_1$cell 
ctrp2_1$cell <- NULL
ctrp2_1 <- as.data.frame(ctrp2_1)

ctrp2_1 <- impute.knn(as.matrix(ctrp2_1))$data
```

```{r}
gCSI_1 <- gCSI

rownames(gCSI_1) <- gCSI_1$cells 
gCSI_1$cells <- NULL
gCSI_1 <- as.data.frame(gCSI_1)

gCSI_1 <- impute.knn(as.matrix(gCSI_1))$data
```

```{r}
FORALL_1 <- FORALL

rownames(FORALL_1) <- FORALL_1$cells 
FORALL_1$cells <- NULL
FORALL_1 <- as.data.frame(FORALL_1)

FORALL_1 <- impute.knn(as.matrix(FORALL_1))$data
```

```{r}
beatAML_1 <- beatAML

rownames(beatAML_1) <- beatAML_1$cells 
beatAML_1$cells <- NULL
beatAML_1 <- as.data.frame(beatAML_1)

beatAML_1 <- impute.knn(as.matrix(beatAML_1))$data
```

```{r}
tavor_1 <- tavor

rownames(tavor_1) <- tavor_1$cell 
tavor_1$cell <- NULL
tavor_1 <- as.data.frame(tavor_1)

tavor_1 <- impute.knn(as.matrix(tavor_1))$data
```

## gdsc1
calculate:
```{r}
# # UMAP
# gdsc_umap <- umap(gdsc1_1) 
# # PCA
# TSNE
with_seed(123, gdsc_tsne <- Rtsne(t(gdsc1_1), dims = 2, 
                                  pca = TRUE,theta = 0.0,max_iter = 5000,perplexity = 25))

gdsc_tsne <- as.data.frame(gdsc_tsne$Y)
colnames(gdsc_tsne) <- c("TSNE1", "TSNE2")
rownames(gdsc_tsne) <- colnames(gdsc1_1)
gdsc_tsne$Drugs <- rownames(gdsc_tsne)
gdsc_tsne <- merge(gdsc_tsne,
                      gdsc_drug_rename,
                      by.x = "Drugs",
                      by.y = "old")
gdsc_tsne <- merge(gdsc_tsne,
                      gdsc_drug_anno,
                      by.x = "new",
                      by.y = "DRUG_NAME2")
tmp$dupli <- gdsc_tsne$new[duplicated(gdsc_tsne$new)]
tmp$dupli
```

```{r}
gdsc_tsne <- gdsc_tsne[-c(29,31),]
gdsc_tsne[30,]$TARGET_PATHWAY <- "IGF1R/RTK signaling"
```

```{r}
gdsc1_tsne <- gdsc_tsne
```


```{r}
p <- ggplot(data = gdsc_tsne, 
            aes(x = TSNE1, 
                y = TSNE2,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=TARGET_PATHWAY)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("ggsci::default_igv"))
p
```

```{r}
p_tsne_gdsc1 <- p
```


```{r}
ggplotly(p_tsne_gdsc1)
```


```{r}
tmp$for_label <- gdsc1_tsne[gdsc1_tsne$TARGET_PATHWAY %in% "Apoptosis regulation",]$Drugs
for_label1 <- gdsc1_tsne[gdsc1_tsne$Drugs %in% tmp$for_label,]
```


```{r}
p_gdsc1_tsne <- p +
  geom_point(size = 4, shape = 1, data = for_label1) +
  ggrepel::geom_label_repel(
    aes(label = Drugs),
    data = for_label1,
    color="black",
    max.overlaps = Inf,
    min.segment.length = 0,
    nudge_y      = -0.2,
   direction    = "y",
   hjust        = 1,
   segment.size = 0.1,
   segment.linetype = 6,
   segment.curvature = -0.1,
   max.iter = 1000000,
   max.time = 10,
   nudge_x = for_label1[which(for_label1$TSNE1 < 0),]$TSNE1 + 1.5*min(for_label1$TSNE1),
  )
p_gdsc1_tsne
```

## gdsc2
gdsc2
calculate:
```{r}
# # UMAP
# gdsc_umap <- umap(gdsc1_1) 
# # PCA
# gdsc_pca <- PCA(gdsc1_1) 
# gdsc_pca <-  get_pca_ind(gdsc_pca)
# gdsc_pca <- gdsc_pca$coord
# gdsc_pca <- gdsc_pca[,c(1,2)]
# TSNE
with_seed(123, gdsc_tsne <- Rtsne(t(gdsc2_1), dims = 2, 
                                  pca = TRUE,theta = 0.0,max_iter = 5000,perplexity = 25))

gdsc_tsne <- as.data.frame(gdsc_tsne$Y)
colnames(gdsc_tsne) <- c("TSNE1", "TSNE2")
rownames(gdsc_tsne) <- colnames(gdsc2_1)
gdsc_tsne$Drugs <- rownames(gdsc_tsne)
gdsc_tsne <- merge(gdsc_tsne,
                      gdsc_drug_rename,
                      by.x = "Drugs",
                      by.y = "old")
gdsc_tsne <- merge(gdsc_tsne,
                      gdsc_drug_anno,
                      by.x = "new",
                      by.y = "DRUG_NAME2")
tmp$dupli <- gdsc_tsne$new[duplicated(gdsc_tsne$new)]
tmp$dupli
```

```{r}
gdsc_tsne <- gdsc_tsne[-c(15,20,31,45,51,86),]
gdsc_tsne$TARGET_PATHWAY[gdsc_tsne$Drugs %in% c("DASATINIB",
                                                      "GSK1904529A",
                                                      "LAPATINIB",
                                                      "SORAFENIB")] <- 
  c("kinases & RTK signaling",
    "IGF1R/RTK signaling",
    "EGFR/RTK signaling",
    "kinases & RTK signaling")

gdsc2_tsne <- gdsc_tsne
```

```{r}
p <- ggplot(data = gdsc2_tsne, 
            aes(x = TSNE1, 
                y = TSNE2,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=TARGET_PATHWAY)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("ggsci::default_igv"))
p
```

```{r}
p_tsne_gdsc2 <- p
```


```{r}
tmp$for_label_med <- gdsc2_overall[order(gdsc2_overall$Median),] %>% 
  head(10) %>% select(Drugs) %>% unlist() 
for_label2 <- gdsc_tsne[gdsc_tsne$Drugs %in% tmp$for_label_med,]
```


```{r}
p_gdsc2_tsne <- p +
  geom_point(size = 3, shape = 1, data = for_label2) +
  ggrepel::geom_label_repel(
    aes(label = Drugs),
    data = for_label2,
    color="black",
    max.overlaps = Inf,
    min.segment.length = 0,
    nudge_y      = -0.2,
   direction    = "y",
   hjust        = 1,
   segment.size = 0.1,
   segment.linetype = 6,
   segment.curvature = -0.1,
   max.iter = 1000000,
   max.time = 10,
   nudge_x = for_label[which(for_label$TSNE1 < 0),]$TSNE1 + 1.5*min(for_label$TSNE1),
  )
p_gdsc2_tsne
```

```{r}
# ggsave(p_gdsc1_tsne, 
#        filename = "Output/Steps/R03/p_gdsc1_tsne.png", device = "png", width = 10, height = 10, dpi = 300)
# 
# ggsave(p_gdsc2_tsne, 
#        filename = "Output/Steps/R03/p_gdsc2_tsne.png", device = "png", width = 10, height = 10, dpi = 300)
```

## ctrp1
```{r}
with_seed(123, ctrp_tsne <- Rtsne(t(ctrp1_1), dims = 2, 
                                  pca = TRUE,theta = 0.0,max_iter = 5000,perplexity = 25))

ctrp_tsne <- as.data.frame(ctrp_tsne$Y)
colnames(ctrp_tsne) <- c("TSNE1", "TSNE2")
rownames(ctrp_tsne) <- colnames(ctrp1_1)
ctrp_tsne$Drugs <- rownames(ctrp_tsne)
```

```{r}
ctrp_tsne1 <- merge(ctrp_tsne,
                       drug_anno[,1:2], by.x = "Drugs",
                       by.y = "Name")
ctrp_tsne2 <- ctrp_tsne[!ctrp_tsne$Drugs %in% drug_anno$Name,]
ctrp_tsne2$MOA <- "Unknown"

ctrp_tsne <- rbind(ctrp_tsne1,
                       ctrp_tsne2)
ctrp1_tsne <- ctrp_tsne
```

```{r}
p <- ggplot(data = ctrp1_tsne, 
            aes(x = TSNE1, 
                y = TSNE2,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=MOA)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("palettesForR::Web")) + theme(legend.position = "none")
p
```

```{r}
p_tsne_ctrp1 <- p
```

## ctrp2
```{r}
with_seed(123, ctrp_tsne <- Rtsne(t(ctrp2_1), dims = 2, 
                                  pca = TRUE,theta = 0.0,max_iter = 5000,perplexity = 25))

ctrp_tsne <- as.data.frame(ctrp_tsne$Y)
colnames(ctrp_tsne) <- c("TSNE1", "TSNE2")
rownames(ctrp_tsne) <- colnames(ctrp2_1)
ctrp_tsne$Drugs <- rownames(ctrp_tsne)
```

```{r}
ctrp_tsne1 <- merge(ctrp_tsne,
                       drug_anno[,1:2], by.x = "Drugs",
                       by.y = "Name")
ctrp_tsne2 <- ctrp_tsne[!ctrp_tsne$Drugs %in% drug_anno$Name,]
ctrp_tsne2$MOA <- "Unknown"

ctrp_tsne <- rbind(ctrp_tsne1,
                       ctrp_tsne2)
ctrp2_tsne <- ctrp_tsne
```

```{r}
p <- ggplot(data = ctrp2_tsne, 
            aes(x = TSNE1, 
                y = TSNE2,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=MOA)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("palettesForR::Web")) + theme(legend.position = "none")
p
```

```{r}
p_tsne_ctrp2 <- p
```

## tavor
```{r}
with_seed(123, tavor_tsne <- Rtsne(t(tavor_1), dims = 2, 
                                  pca = TRUE,theta = 0.0,max_iter = 5000,perplexity = 5))

tavor_tsne <- as.data.frame(tavor_tsne$Y)
colnames(tavor_tsne) <- c("TSNE1", "TSNE2")
rownames(tavor_tsne) <- colnames(tavor_1)
tavor_tsne$Drugs <- rownames(tavor_tsne)
```

```{r}
tavor_tsne1 <- merge(tavor_tsne,
                       drug_anno[,1:2], by.x = "Drugs",
                       by.y = "Name")
tavor_tsne2 <- tavor_tsne[!tavor_tsne$Drugs %in% drug_anno$Name,]
tavor_tsne2$MOA <- "Unknown"

tavor_tsne <- rbind(tavor_tsne1,
                       tavor_tsne2)
```

```{r}
p <- ggplot(data = tavor_tsne, 
            aes(x = TSNE1, 
                y = TSNE2,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=MOA)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("ggsci::default_igv")) + theme(legend.position = "none")
p
```

```{r}
p_tsne_tavor <- p
```

## gCSI
```{r}
with_seed(123, gCSI_tsne <- Rtsne(t(gCSI_1), dims = 2, 
                                  pca = TRUE,theta = 0.0,max_iter = 5000,perplexity = 5))

gCSI_tsne <- as.data.frame(gCSI_tsne$Y)
colnames(gCSI_tsne) <- c("TSNE1", "TSNE2")
rownames(gCSI_tsne) <- colnames(gCSI_1)
gCSI_tsne$Drugs <- rownames(gCSI_tsne)
```

```{r}
gCSI_tsne1 <- merge(gCSI_tsne,
                       drug_anno[,1:2], by.x = "Drugs",
                       by.y = "Name")
gCSI_tsne2 <- gCSI_tsne[!gCSI_tsne$Drugs %in% drug_anno$Name,]
gCSI_tsne2$MOA <- "Unknown"

gCSI_tsne <- rbind(gCSI_tsne1,
                       gCSI_tsne2)
```

```{r}
p <- ggplot(data = gCSI_tsne, 
            aes(x = TSNE1, 
                y = TSNE2,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=MOA)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("ggsci::default_igv")) + theme(legend.position = "none")
p
```

```{r}
p_tsne_gCSI <- p
```

## BeatAML
```{r}
with_seed(123, BeatAML_tsne <- Rtsne(t(beatAML_1), dims = 2, 
                                  pca = TRUE,theta = 0.0,max_iter = 5000,perplexity = 25))

BeatAML_tsne <- as.data.frame(BeatAML_tsne$Y)
colnames(BeatAML_tsne) <- c("TSNE1", "TSNE2")
rownames(BeatAML_tsne) <- colnames(beatAML_1)
BeatAML_tsne$Drugs <- rownames(BeatAML_tsne)
```

```{r}
BeatAML_tsne1 <- merge(BeatAML_tsne,
                       drug_anno[,1:2], by.x = "Drugs",
                       by.y = "Name")
BeatAML_tsne2 <- BeatAML_tsne[!BeatAML_tsne$Drugs %in% drug_anno$Name,]
BeatAML_tsne2$MOA <- "Unknown"

BeatAML_tsne <- rbind(BeatAML_tsne1,
                       BeatAML_tsne2)
```

```{r}
p <- ggplot(data = BeatAML_tsne, 
            aes(x = TSNE1, 
                y = TSNE2,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=MOA)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("ggsci::default_igv")) + theme(legend.position = "none")
p
```

```{r}
p_tsne_beatAML <- p
```

## FORALL
```{r}
with_seed(123, forall_tsne <- Rtsne(t(FORALL_1), dims = 2, 
                                  pca = TRUE,theta = 0.0,max_iter = 5000,perplexity = 25, check_duplicates = FALSE))

forall_tsne <- as.data.frame(forall_tsne$Y)
colnames(forall_tsne) <- c("TSNE1", "TSNE2")
rownames(forall_tsne) <- colnames(FORALL_1)
forall_tsne$Drugs <- rownames(forall_tsne)
```

```{r}
forall_tsne <- merge(forall_tsne,
                       FORALL_druganno_leu[,c(1,4)], by.x = "Drugs",
                       by.y = "Drug name")
```

```{r}
p <- ggplot(data = forall_tsne, 
            aes(x = TSNE1, 
                y = TSNE2,
                label = Drugs)) +
  geom_point(alpha=0.4, size=3.5, 
             aes(color=`Drug Class`)) + theme_bw() + 
  scale_color_manual(values = paletteer::paletteer_d("ggsci::default_igv")) 
p
```

```{r}
p_tsne_forall <- p
```

# Compare Drugs
## Preprocess
```{r}
load(file = "Output/Steps/R01/gdsc_leu_v2.Rda")
```

```{r}
head(gdsc_anno_leu)
```

```{r}
gdsc_anno_leu$Name2 <- gsub("-", "", gdsc_anno_leu$Name)

# gdsc1_1 <- as.data.frame(t(gdsc1_1))
# gdsc1_1$COSMIC_ID <- rownames(gdsc1_1)
gdsc1_check_drugs <- merge(gdsc1_drug_leu2,
                           gdsc_anno_leu[,c(1,3,5)],
                           by.x = "COSMIC_ID",
                           by.y = "Name2")
```

## Similar results but diff targets
THZ-2-102-1: CDK7
YM-155: BIRC5

THZ1+ >> BIRC5-
https://pubmed.ncbi.nlm.nih.gov/30145799/

The boxplot distribution of these two drugs.

```{r}
gdsc1_check_drugs2 <- gdsc1_check_drugs[,c(
  "Barcode", "Source2", "COSMIC_ID", "YM-155", "THZ-2-102-1"
)]
# colnames(gdsc1_check_drugs2)[4] <- "DrugAUC1"
# colnames(gdsc1_check_drugs2)[5] <- "DrugAUC2"
# gdsc1_check_drugs2 <- na.omit(gdsc1_check_drugs2)

gdsc1_check_drugs2 <- na.omit(gdsc1_check_drugs2)

tmp$levels <- gdsc1_check_drugs2[order(gdsc1_check_drugs2$`YM-155`),]$Barcode %>% 
  unique()

gdsc1_check_drugs_tmp <- gather(data = gdsc1_check_drugs2[,c(3:5)],
       key = DrugName,
       value = DrugAUC,
       - COSMIC_ID)

gdsc1_check_drugs2 <- merge(
  gdsc1_check_drugs2[,-c(4:5)],
  gdsc1_check_drugs_tmp, by = "COSMIC_ID"
)

gdsc1_check_drugs2$Barcode <- factor(gdsc1_check_drugs2$Barcode,
                                       levels = tmp$levels)
```

```{r}
ggbarplot(data = gdsc1_check_drugs2, 
          x = "Barcode",
          y = "DrugAUC", fill = "DrugName", position = position_dodge()) + theme(
            axis.text.x = element_text(angle = 90)
          )
```


## Similar targets but diff effects
mTOR: 
torin2: MTOR, ATM, ATR, DNAPK
TEMSIROLIMUS: MTOR

## low median and low sd drugs
Mean these drugs are stable.
torin2 in gdsc1 for example.

ym-155 for both gdsc1 and gdsc2.

```{r}
gdsc1_check_drugs2 <- gdsc1_check_drugs[,c(
  "Barcode", "YM-155", "Source2", "COSMIC_ID"
)]
colnames(gdsc1_check_drugs2)[2] <- "DrugAUC"
gdsc1_check_drugs2 <- na.omit(gdsc1_check_drugs2)

gdsc1_check_drugs2 <- gdsc1_check_drugs2[order(gdsc1_check_drugs2$DrugAUC),]
gdsc1_check_drugs2$Barcode <- factor(gdsc1_check_drugs2$Barcode,
                                     levels = unique(gdsc1_check_drugs2$Barcode))
```


```{r}
ggbarplot(data = gdsc1_check_drugs2, 
          x = "Barcode",
          y = "DrugAUC", fill = "Source2") + theme(
            axis.text.x = element_text(angle = 90)
          )
```


# Intersection && Correspondence
```{r}
gdsc_overlap <- intersect(gdsc1_overall$Drugs, gdsc2_overall$Drugs)
gdsc_overlap
```

```{r}
for_label1[for_label1$Drugs %in% gdsc_overlap,]
```


# Save

## Raw
```{r}
ctrp1 <- ctrp1_drug_leu2
rownames(ctrp1) <- ctrp1$DepMap_ID; ctrp1$DepMap_ID <- NULL

ctrp2 <- ctrp2_drug_leu2
rownames(ctrp2) <- ctrp2$DepMap_ID; ctrp2$DepMap_ID <- NULL

gdsc1 <- gdsc1_drug_leu2
rownames(gdsc1) <- gdsc1$COSMIC_ID; gdsc1$COSMIC_ID <- NULL

gdsc2 <- gdsc2_drug_leu2
rownames(gdsc2) <- gdsc2$COSMIC_ID; gdsc2$COSMIC_ID <- NULL

```

```{r}
save(ctrp1,
     ctrp2,
     gdsc1,
     gdsc2,
     file = "Output/Steps/R03/shiny/leu_drugs_shiny.Rda")
```

## SD
```{r}
gdsc1_sd_df <- gdsc1_overall
gdsc1_sd_df$new <- NULL
gdsc2_sd_df <- gdsc2_overall
gdsc2_sd_df$new <- NULL
ctrp1_sd_df <- ctrp1_overall
ctrp2_sd_df <- ctrp2_overall
```

```{r}
save(gdsc1_sd_df,
     gdsc2_sd_df,
     ctrp1_sd_df,
     ctrp2_sd_df,
     file = "Output/Steps/R03/shiny/leu_drugs_sd.Rda")
```

plot:
```{r}
save(p_sd_gdsc1,
     p_sd_gdsc2,
     p_sd_ctrp1,
     p_sd_ctrp2,
     p_sd_gCSI,
     p_sd_tavor,
     p_sd_BeatAML,
     p_sd_FORALL,
     file = "Output/Steps/R03/shiny/leu_drugs_sd_plot.Rda")
```

## tsne
```{r}
gdsc1_tsne$new <- NULL
gdsc2_tsne$new <- NULL
```

```{r}
save(gdsc1_tsne,
     gdsc2_tsne,
     ctrp1_tsne,
     ctrp2_tsne,
     BeatAML_tsne,
     tavor_tsne,
     forall_tsne,
     gCSI_tsne,
     file = "Output/Steps/R03/shiny/leu_drugs_tsne.Rda")
```

```{r}
save(
  p_tsne_ctrp1,
  p_tsne_ctrp2,
  p_tsne_gdsc1,
  p_tsne_gdsc2,
  p_tsne_beatAML,
  p_tsne_gCSI,
  p_tsne_forall,
  p_tsne_tavor,
  file = "Output/Steps/R03/shiny/leu_drugs_tsne_plot.Rda"
)
```




